---
title:'Deconstructing the (un)affordability of clean cooking fuels'
subtitle: "TMLE Immediate Impact - ITT: Adjusted for time & not"

output: pdf_document
---

```{r - packages and data}
library(SuperLearner)
library(ltmle)
library(tmle)
library(dplyr)
library(tidyr)
library(writexl)
library(readxl)
set.seed(252)
# load in data df_all
```

##TMLE Analysis: Organized as tmle.result.lead.controlling for time.parameter_of_interest.hypothesis_number.sub_hypothesis_number 

#Parameter of interest (PoI): Immediate Impact=1;
#Hypothesis: Exclusive LPG Use=3; Habitual Use = 3.2; Ocassional use = 3.3; No LPG use = 3.4; kg of firewood=4.1; kg of charcoal=4.2

```{r}
df <- df_all
df$outcome <- df$lead_exclusive_lpg_user
df<-na.omit(df[,c('hh_id','visit_number','intent_tr','outcome')])
W<-df[c('visit_number')]
tmle.results.lead.time.1.3 =tmle(Y=df$outcome, A=df$intent_tr, W=W,
                          Q.SL.library = c("SL.glm"), 
                          g.Delta.SL.library =  c("SL.glm"),
                          gform  = "A~1",
                          family = "binomial", id=df$hh_id)
summary(tmle.results.lead.time.1.3)
tmle.results.lead.time.1.3$estimates$ATE$psi
tmle.results.lead.time.1.3$estimates$ATE$pvalue
```


```{r}
df <- df_all
df$outcome <- df$lead_habitual_lpg_user
df<-na.omit(df[,c('hh_id','visit_number','intent_tr','outcome')])
W<-df[c('visit_number')]
tmle.results.lead.time.1.3.2 =tmle(Y=df$outcome, A=df$intent_tr, W=W,
                          Q.SL.library = c("SL.glm"), 
                          g.Delta.SL.library =  c("SL.glm"),
                          gform  = "A~1",
                          family = "binomial", id=df$hh_id)
summary(tmle.results.lead.time.1.3.2)
tmle.results.lead.time.1.3.2$estimates$ATE$psi
tmle.results.lead.time.1.3.2$estimates$ATE$pvalue
```

```{r}
df <- df_all
df$outcome <- df$lead_ocassional_lpg_user
df<-na.omit(df[,c('hh_id','visit_number','intent_tr','outcome')])
W<-df[c('visit_number')]
tmle.results.lead.time.1.3.3 =tmle(Y=df$outcome, A=df$intent_tr, W=W,
                          Q.SL.library = c("SL.glm"), 
                          g.Delta.SL.library =  c("SL.glm"),
                          gform  = "A~1",
                          family = "binomial", id=df$hh_id)
summary(tmle.results.lead.time.1.3.3)
round(tmle.results.lead.time.1.3.3$estimates$ATE$psi,2)
tmle.results.lead.time.1.3.3$estimates$ATE$pvalue
```

```{r}
df <- df_all
df$outcome <- df$lead_no_lpg_user
df<-na.omit(df[,c('hh_id','visit_number','intent_tr','outcome')])
W<-df[c('visit_number')]
tmle.results.lead.time.1.3.4 =tmle(Y=df$outcome, A=df$intent_tr, W=W,
                          Q.SL.library = c("SL.glm"), 
                          g.Delta.SL.library =  c("SL.glm"),
                          gform  = "A~1",
                          family = "binomial", id=df$hh_id)
summary(tmle.results.lead.time.1.3.4)
tmle.results.lead.time.1.3.4$estimates$ATE$psi
tmle.results.lead.time.1.3.4$estimates$ATE$pvalue
```

```{r}
df <- df_all
df$outcome <- df$lead_total_kg_firewood_per_day
df<-na.omit(df[,c('hh_id','visit_number','intent_tr','outcome')])
W<-df[c('visit_number')]
tmle.results.lead.time.1.4.1 =tmle(Y=df$outcome, A=df$intent_tr, W=W,
                          Q.SL.library = c("SL.glm"), 
                          g.Delta.SL.library =  c("SL.glm"),
                          gform  = "A~1",
                          family = "gaussian", id=df$hh_id)
summary(tmle.results.lead.time.1.4.1)
tmle.results.lead.time.1.4.1$estimates$ATE$psi
tmle.results.lead.time.1.4.1$estimates$ATE$pvalue
```

```{r}
df <- df_all
df$outcome <- df$lead_total_kg_charcoal_per_day
df<-na.omit(df[,c('hh_id','visit_number','intent_tr','outcome')])
W<-df[c('visit_number')]
tmle.results.lead.time.1.4.2 =tmle(Y=df$outcome, A=df$intent_tr, W=W,
                          Q.SL.library = c("SL.glm"), 
                          g.Delta.SL.library =  c("SL.glm"),
                          gform  = "A~1",
                          family = "gaussian", id=df$hh_id)
summary(tmle.results.lead.time.1.4.2)
tmle.results.lead.time.1.4.2$estimates$ATE$psi
tmle.results.lead.time.1.4.2$estimates$ATE$pvalue
```



## TMLE Analysis, not controlling for time 

#note that W is "hh_id" times 1 as we did not include any covariates as all were balanced (Table S1)

```{r}
df <- df_all
df$outcome <- df$lead_exclusive_lpg_user
df<-na.omit(df[,c('hh_id','visit_number','intent_tr','outcome')])
W<-df[c('hh_id')]*1
tmle.results.lead.no.time.1.3 =tmle(Y=df$outcome, A=df$intent_tr, W=W,
                          Q.SL.library = c("SL.glm"), 
                          g.Delta.SL.library =  c("SL.glm"),
                          gform  = "A~1",
                          family = "binomial", id=df$hh_id)
summary(tmle.results.lead.no.time.1.3)
tmle.results.lead.no.time.1.3$estimates$ATE$psi
tmle.results.lead.no.time.1.3$estimates$ATE$pvalue
```

```{r}
df <- df_all
df$outcome <- df$lead_habitual_lpg_user
df<-na.omit(df[,c('hh_id','visit_number','intent_tr','outcome')])
W<-df[c('hh_id')]*1
tmle.results.lead.no.time.1.3.2 =tmle(Y=df$outcome, A=df$intent_tr, W=W,
                          Q.SL.library = c("SL.glm"), 
                          g.Delta.SL.library =  c("SL.glm"),
                          gform  = "A~1",
                          family = "binomial", id=df$hh_id)
summary(tmle.results.lead.no.time.1.3.2)
tmle.results.lead.no.time.1.3.2$estimates$ATE$psi
tmle.results.lead.no.time.1.3.2$estimates$ATE$pvalue
```

```{r}
df <- df_all
df$outcome <- df$lead_ocassional_lpg_user
df<-na.omit(df[,c('hh_id','visit_number','intent_tr','outcome')])
W<-df[c('hh_id')]*1
tmle.results.lead.no.time.1.3.3 =tmle(Y=df$outcome, A=df$intent_tr, W=W,
                          Q.SL.library = c("SL.glm"), 
                          g.Delta.SL.library =  c("SL.glm"),
                          gform  = "A~1",
                          family = "binomial", id=df$hh_id)
summary(tmle.results.lead.no.time.1.3.3)
round(tmle.results.lead.no.time.1.3.3$estimates$ATE$psi,2)
tmle.results.lead.no.time.1.3.3$estimates$ATE$pvalue
```

```{r}
df <- df_all
df$outcome <- df$lead_no_lpg_user
df<-na.omit(df[,c('hh_id','visit_number','intent_tr','outcome')])
W<-df[c('hh_id')]*1
tmle.results.lead.no.time.1.3.4 =tmle(Y=df$outcome, A=df$intent_tr, W=W,
                          Q.SL.library = c("SL.glm"), 
                          g.Delta.SL.library =  c("SL.glm"),
                          gform  = "A~1",
                          family = "binomial", id=df$hh_id)
summary(tmle.results.lead.no.time.1.3.4)
tmle.results.lead.no.time.1.3.4$estimates$ATE$psi
tmle.results.lead.no.time.1.3.4$estimates$ATE$pvalue
```

```{r}
df <- df_all
df$outcome <- df$lead_total_kg_firewood_per_day
df<-na.omit(df[,c('hh_id','visit_number','intent_tr','outcome')])
W<-df[c('hh_id')]*1
tmle.results.lead.no.time.1.4.1 =tmle(Y=df$outcome, A=df$intent_tr, W=W,
                          Q.SL.library = c("SL.glm"), 
                          g.Delta.SL.library =  c("SL.glm"),
                          gform  = "A~1",
                          family = "gaussian", id=df$hh_id)
summary(tmle.results.lead.no.time.1.4.1)
tmle.results.lead.no.time.1.4.1$estimates$ATE$psi
tmle.results.lead.no.time.1.4.1$estimates$ATE$pvalue
```

```{r}
df <- df_all
df$outcome <- df$lead_total_kg_charcoal_per_day
df<-na.omit(df[,c('hh_id','visit_number','intent_tr','outcome')])
W<-df[c('hh_id')]*1
tmle.results.lead.no.time.1.4.2 =tmle(Y=df$outcome, A=df$intent_tr, W=W,
                          Q.SL.library = c("SL.glm"), 
                          g.Delta.SL.library =  c("SL.glm"),
                          gform  = "A~1",
                          family = "gaussian", id=df$hh_id)
summary(tmle.results.lead.no.time.1.4.2)
tmle.results.lead.no.time.1.4.2$estimates$ATE$psi
tmle.results.lead.no.time.1.4.2$estimates$ATE$pvalue
```
